\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-10-23 paper/ms.tex
Reran RJObject_1DMixture because of previous bug in Laplace
Figure with the high posterior weight points

\subsection{Mixture model results}
The data and the posterior mean fit are shown
in Figure~\ref{fig:galaxies} and the posterior distribution for
$N$ is shown in Figure~\ref{fig:galaxies_N}.
The marginal likelihood was $\ln(Z) = -241.7$, and
the information (measured in nats) was $\mathcal{H} = 32.0$.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.7\textwidth]{figures/galaxies_fig3.pdf}
\caption{The log-likelihood and posterior weights as a function
of compression $X$ for the galaxy data. There are phase changes
\citep{skilling2006nested} for which Nested Sampling is the best known
solution.
\label{fig:galaxies_fig3}}
\end{figure}

>>>>

\subsection{Mixture model results}
The data and the posterior mean fit are shown
in Figure~\ref{fig:galaxies} and the posterior distribution for
$N$ is shown in Figure~\ref{fig:galaxies_N}.
The marginal likelihood was $\ln(Z) = -232.2$, and
the information (measured in nats) was $\mathcal{H} = 29.5$.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.7\textwidth]{figures/galaxies_fig3.pdf}
\caption{The log-likelihood and posterior weights as a function
of compression $X$ for the galaxy data. There are phase changes
\citep{skilling2006nested} for which Nested Sampling is the best known
solution. There are some points with high posterior weight at the left
of the plot, but there are so few of them that they make up a trivial
fraction of the posterior mass. In practice, however, it is worth
re-running with more levels to verify that a second peak is not forming.
\label{fig:galaxies_fig3}}
\end{figure}
